Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-26 5-Analysis.tex

First, the federation approach is mainly based on modeling relationships among several models, independently of abstraction levels and model architectures.
The next step in our approach, we try to take into account the reusability of the relationships by identifying the meaning, or semantics, associated with each relationship, in a goal of concept reification with their behavior. The last step is to organize or structure these concepts to improve reusability and extensibility, to create VirtualModels in our Openflexo framework.

Like any modeling approaches, these different steps could also be achieved in any order. But our goal during the challenge requirement analysis remains to lead to define a FML Virtual Models architecture as a federation of virtualmodels. As shown in figure~\ref{fig:MultilevelArchitecture}, we developped two metamodels (Base and ACME processes abstractions) instantiatied by two models (XSure and ACME processes). This follows the way the challenge is presented and this organisation allows for the possibility of easy extensions.

>>>>

First, the federation approach is mainly based on modeling relationships among several models, independently of abstraction levels and model architectures.
During the next step of our approach, we try to take into account the reusability of the relationships by identifying the meaning, the semantics, associated with each relationship, in a goal of concept reification with their behavior. The last step is to organize or structure these concepts to improve reusability and extensibility, to create VirtualModels in our Openflexo framework.

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). This follows the way the challenge is presented and this organisation allows for the possibility of easy extensions.

### 2021-05-26 8-Discussion.tex

@@

  \noteJC{pas trop clair pour moi pour le moment}

@@

>>>>

% Assessment of the Modeling Solution: discussing choices made, pointing out potential compromises / deficiencies

@@

  \noteJC{pas trop clair pour moi pour le moment -> N/A}

@@

\todo[inline]{verification de cohérence syntaxique (cardinalités, type des instances) et des contraintes métier (comportements écrits par les humains) à la volée + validation manuelle ; typage ? ; pas d'analyseur statique ; vérif de la structure des contraintes/bonne forme des contraintes par rapport à la structure des modèles (exemple binding pas valide)}
